\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-05-26 AffineLieAlgebras/InformalNotes/article.tex
More notes from V.D.

If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}. We study the example of $\hat{A}_1\subset \hat{A}_2\subset\hat{A}_{3}$ in the section \ref{sec:non-maxim-conf}.

@@

\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$. The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.

There exist three level one dominant weights in the weight space of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\bot}$ and the algebra $\mathfrak{a}_{\bot}$ are empty.

@@

The set of the anomalous weights of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.

\begin{figure}[h!tb]
  \centering
  \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
  \caption{The anomalous weights of the $(0,0;1;0)$ representation of the algebra $\hat{A_2}$}
  \label{fig:affine_A2_anom_point}
\end{figure}

According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$.
The result of these calculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Then we construct ``the fan'' and use the recurrent relations to compute the anomalous branching coefficients.

Using the definition (\ref{fan-defined}) we get the following set of
the weights $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
Here we restricted the calculations to the first eight grades.
\begin{figure}[p]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

@@

We see that inside the main Weyl chamber of $\hat{A}_1$, which is dotted at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)]}.
\end{equation}

For the other level one dominant weights of $\hat{A}_2$ we get the trivial
branching 
\begin{eqnarray}
  \label{eq:44}
   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
\end{eqnarray}

Using this result the modular-invariant partition function is easily found,
\begin{equation}
  \label{eq:45}
  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
\end{equation}

>>>>

If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}.

@@

\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$. The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.

There exist three level one dominant weights in the weight space of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.

@@

The set of the anomalous weights of this representation  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.

\begin{figure}[h!tb]
  \centering
  \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
  \label{fig:affine_A2_anom_point}
\end{figure}

Using the definition (\ref{fan-defined})  we construct ``the fan'' $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}). 
Here we restricted the calculations to the first eight grades.
\begin{figure}[p]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

The next step is to project the anomalous weights to $P_{\aht A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

@@

We see that inside the main Weyl chamber of $\hat{A}_1$, which is dotted at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

For the other level one irreducible modules of $\hat{A}_2$ we get the trivial
branching 
\begin{eqnarray}
  \label{eq:44}
   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
\end{eqnarray}

Using these results the modular-invariant partition function is easily found,
\begin{equation}
  \label{eq:45}
  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
\end{equation}
